Estimating Gaze Duration Error from Eye Tracking Data

### 2023-03-01 paper/paper.tex
Paper update

The algorithm consists of two core steps, first estimating the distrubtion of measurements
for a given true duration. Secondly, inverting this into the distribution of true
gaze durtions for a given measurement. Note, that the algorithm requires that the area of
interest be defined as a fixed bounding box and that the distributions are estimated for
a fixed session length. This session length is the total period of time that the area of
interest was in a subject's field of view, and thus represents the maximum possible gaze
duration.

@@

The bulk of the work is done by two functions inside the simulation loop. The first function
$generatePath(d,l,s)$ takes a true gaze duration (for that simulation iteration) the location
of the gaze target and the viewing session length. It then
generates a random path of fixation points that is compatible with those parameters.
The second function 
$generateMeasurement(p,l,C)$, takes the path, target location and the eye tracking calibration 
data and produces a sample of measured attention time. It does this by using the calibration data to sample
fixation errors and apply them to the path data. The noisy path data is then used to determine
the estimated gaze duration by looking at the number of fixation points that intersect with the target
location.
Repeated application of this process for a given value of $d$ produces multiple samples of $\hat{d}$
for that true gaze duration. Repeating the process over different 
values of $d$ allows us to populate a two dimensional array where the first dimension is the
true duration and the second the estimated duration. Note that our probability distribution is discrete
because we restrict ourselves to sampling over a set of fixed time period increments ($i$) 
between zero and the session length.

@@

The algorithm described in the preceding sections has been implemented as an open source python 
package called \textit{gazerr}. 
It can be used as a software library, exposing functions for calculating the probability densities,
or it can deployed as a command line application. 
The source code is available on GitHub and the python package can be installed from PyPi.

The source repository for the \textit{gazerr} application also contains a series of 
scripts for generating data sets and running the experiments outlined in the next 
section. Full details available in the package \textit{README} file.

@@

We include these biased calibration datasets as they are consistent with both our 
observations of real eye tracking data and what is found in the literature\cite{}.
We use this synthetic data creation in order to explore the extent to which different
patterns in error, bias and precision affects gaze duration measurements.

>>>>

The algorithm consists of two core steps, first estimating the distrubtion of measurements
for a given true duration. Secondly, inverting this into the distribution of true
gaze durations for a given measurement. Note, that the algorithm requires that the area of
interest be defined as a fixed bounding box and that the distributions are estimated for
a fixed session length. This session length is the total period of time that the area of
interest was in a subject's field of view, and thus represents the maximum possible gaze
duration.

@@

The bulk of the work is done by two functions inside the simulation loop. The first function
$generatePath(d,l,s)$ takes a true gaze duration (for that simulation iteration) the location
of the gaze target and the viewing session length. It then
generates a random path of fixation points that is compatible with those parameters.
The second function 
$generateMeasurement(p,l,C)$, takes the path, target location and the eye tracking calibration 
data and produces a sample of measured attention time.
This is achieved by using the calibration data to sample
fixation errors in the proximity of each location within the path and applying them to the path data. 
The noisy path data is then used to determine
the estimated gaze duration by looking at the number of fixation points that intersect with the target
location.
Repeated application of this process for a given value of $d$ produces multiple samples of $\hat{d}$
for that true gaze duration. Repeating the process over different 
values of $d$ allows us to populate a two dimensional array where the first dimension is the
true duration and the second the estimated duration.

Note that our probability distribution is discrete
because we restrict ourselves to sampling over a set of fixed time period increments ($i$) 
between zero and the session length. This restriction is realistic for most machine learning
eye tracking systems as they output fixation points at fixed intervals of time.

@@

The algorithm described in the preceding sections has been implemented as an open source python 
package called \textit{gazerr}. 
It can be used as a software library, exposing functions for calculating the probability densities,
or it can deployed as a command line application. 
The source code is available on GitHub\footnote{https://github.com/playground-xyz/gazerr}
and the python package can be installed from PyPi.\footnote{https://pypi.org/project/gazerr/}

The source repository for the \textit{gazerr} application also contains a series of 
scripts for generating data sets and running the experiments outlined in the next 
section. Full details for the data generation process are available in the 
source code README file.

@@

We include these biased calibration datasets as they are consistent with both our 
observations of real eye tracking data and what is found in the literature\cite{Holmqvist2022}.
We use this synthetic data creation in order to explore the extent to which different
patterns in error, bias and precision affects gaze duration measurements.
